\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-12 WSSSPE4_proposal/WSSSPE4_proposal.tex
Update prior support

\textbf{Gabrielle D.~Allen}
was the PI for two recent workshop awards related to sustainable software. NSF CCF-1551592, made to the University of Illinois for \$88,739 for the period 09/15/2015 to 5/31/2017 supported the workshop on Computational Science \& Engineering Software Sustainability and Productivity Challenges (CSSSPE) which was hosted by NITRD and supported by NSF, DOE and DOD and brought together a very diverse number of agency representatives, software developers and software engineers spanning academia, national labs and industry. A report from this workshop is imminent. 
Allen was also PI for a previous awards supporting WSSSPE2 and WSSSPE3, NSF ACI-1434218, made to the University of Illinois for \$24,758 for the period 5/1/2014 to 4/30/2016. The award funded participation at WSSSPE2 and WSSSPE3 by early career researchers and underrepresented groups.

>>>>

\textbf{Gabrielle D.~Allen}
was the PI for two recent workshop awards related to sustainable software. NSF CCF-1551592, made to the University of Illinois for \$88,739 for the period 09/15/2015 to 5/31/2017 supported the workshop on Computational Science \& Engineering Software Sustainability and Productivity Challenges (CSSSPE) which was hosted by NITRD and supported by NSF, DOE and DOD and brought together a very diverse number of agency representatives, software developers and software engineers spanning academia, national labs and industry. A report from this workshop is imminent. 
Allen was also PI for a previous award supporting WSSSPE2 and WSSSPE3, NSF ACI-1434218, made to the University of Illinois for \$24,758 for the period 5/1/2014 to 4/30/2016.  {\bf Intellectual Merit:} Publications  resulting from the WSSSPE2 and WSSSPE3 workshop include \cite{WSSSPE2-collection, WSSSPE2, WSSSPE3}. {\bf Broader Impacts:} The award funded participation at WSSSPE2 and WSSSPE3 by early career researchers and underrepresented groups.
